Describe and Explore: Using feature-based time series clustering to identify meaningful structures in intensive longitudinal data

### 2023-01-17 methods-and-results.Rmd
:shit: formulas tst
:eyes: render check formulae

\begin{equation}
  Median(X_ij) = \left\{ 
    \begin{array}{ll}
      X \left[ \frac{n+1}{2} \right] & if n is odd \\
      \frac{X \left[ \frac{n}{2} \right] + X \left[ \frac{n}{2} +1 \right]}{2} & if n is even
    \end{array}
\end{equation}

>>>>

\begin{equation} \label{eq:median}
  Median(X_{ij}) = 
    \begin{cases}
      X \left[ \frac{n+1}{2} \right] & \text{if $n$ is odd} \\
      \frac{X \left[ \frac{n}{2} \right] + X \left[ \frac{n}{2} +1 \right]}{2} & \text{if $n$ is even}
    \end{cases}
\end{equation}

For distribution we chose the \textit{Median Absolute Deviation} ($MAD$), where we calculate the $Median$ (as in \eqref{eq:median}) for the absolute deviations of measurement $x$ at time point $t$ for participant $i$ and variable $j$.

\begin{equation} \label{eq:mad}
  MAD(x_{ijt}) = Median(| x_{ijt} - \overline{x_{ij}} |)
\end{equation}

### 2023-01-17 methods-and-results.tex
:shit: formulas tst
:eyes: render check formulae

\begin{equation}
  Median(X_ij) = \left\{ 
    \begin{array}{ll}
      X \left[ \frac{n+1}{2} \right] & if n is odd \\
      \frac{X \left[ \frac{n}{2} \right] + X \left[ \frac{n}{2} +1 \right]}{2} & if n is even
    \end{array}
\end{equation}

>>>>

\begin{equation} \label{eq:median}
  Median(X_{ij}) = 
    \begin{cases}
      X \left[ \frac{n+1}{2} \right] & \text{if $n$ is odd} \\
      \frac{X \left[ \frac{n}{2} \right] + X \left[ \frac{n}{2} +1 \right]}{2} & \text{if $n$ is even}
    \end{cases}
\end{equation}

For distribution we chose the \textit{Median Absolute Deviation}
(\(MAD\)), where we calculate the \(Median\) (as in \eqref{eq:median})
for the absolute deviations of measurement \(x\) at time point \(t\) for
participant \(i\) and variable \(j\).

\begin{equation} \label{eq:mad}
  MAD(x_{ijt}) = Median(| x_{ijt} - \overline{x_{ij}} |)
\end{equation}
